Bayesian statistics for repeated measures

### 2020-10-20 Manuscripts/Manuscript_AM_v1.Rmd
Udpated

x<-seq(0.6,500)
knots <- c(0.25, 0.5, 0.75)
theta <- c(0.6, 0.1, 0.5, 0.2, 0.8, 0.3)
basis<-bs(x,knots=3,degree=1)
y.spline<-basis %*% theta

ggplot(data=ab,aes(x=dt,y=z))+geom_point()
ggplot(data=ab,aes(x=dt,y=zq))+geom_point()

>>>>

# x<-seq(0.6,500)
# knots <- c(0.25, 0.5, 0.75)
# theta <- c(0.6, 0.1, 0.5, 0.2, 0.8, 0.3)
# basis<-bs(x,knots=3,degree=1)
# y.spline<-basis %*% theta
# 
# 
# ggplot(data=ab,aes(x=dt,y=z))+geom_point()
# ggplot(data=ab,aes(x=dt,y=zq))+geom_point()
